plackett_luce_monster

### 2022-07-25 inst/plackett_luce_monster.Rmd
typo

The five nations rugby championship was held from 1910 to 1999 and
file five_nations.txt` shows the order statistic for England (E),
Scotland (S), Ireland (I), Wales (W), and France (F).

>>>>

The five nations rugby championship was held from 1910 to 1999 and
file `five_nations.txt` shows the order statistic for England (E),
Scotland (S), Ireland (I), Wales (W), and France (F).
